---
title: "Testing_VA"
author: "Oren"
date: "9/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(fable)
library(tsibble)
library(dplyr)
library(tidyverse)
library(reshape2)
library(ggplot2)
library(plotly)
library(feasts)
library(imputeTS)
library(tidymodels)
library(skimr)
library(zoo)
library(lubridate)
library(lme4)
library(readr)
library(stringi)
library(reprex)
library(sparklyr)
```



```{r}
zri_df_og <-read_csv("../../data/full_dataset_unscaled.csv")

```

```{r}
length(unique(unlist(zri_df_og[c("City")])))
length(unique(unlist(zri_df_og[c("State")])))
length(unique(unlist(zri_df_og[c("Metro")])))
length(unique(unlist(zri_df_og[c("CountyName")])))

sum(is.na(zri_df_og$CountyName))

zri_df_og %>% group_by(Metro) %>% summarise(Unique_Elements = n_distinct(zip))
```



```{r}
zri_df <- zri_df_og 

zri_df$ym <- yearmonth(zri_df$datetime) 

zri_df <- zri_df %>%
  select(-c(datetime, year, month)) %>% 
  as_tsibble(key = c(zip), index = c(ym))

```

```{r}
zri_for_modeling_base_NOMETRO <- zri_df %>% filter_index(~"2018-12") %>%
  aggregate_key(State/  City/ zip, zri = mean(zri))

fit_base_model_NOMETRO <- zri_for_modeling_base_NOMETRO %>%
  model(base = ETS(zri,
  opt_crit = "mse")) %>%
  reconcile(
    bu = bottom_up(base),
  )
saveRDS(fit_base_model_NOMETRO, file = "fit_base_model_NOMETRO.Rds")
forecast_base_model_NOMETRO <- fit_base_model_NOMETRO %>% forecast(h = "1 year") 


zri_for_modeling_base_alldates <- zri_df  %>%
  aggregate_key(State/ City/ zip, zri = mean(zri))


# fabletools::accuracy(rob_plot, zri_VA_full)
test <- fabletools::accuracy(forecast_base_model_NOMETRO, zri_for_modeling_base_alldates_NOMETRO)
# 
# 
# 
test

mean(test$RMSE)
# # saveRDS(fit_rob, "model.rds")
# fit_rob %>% components()
# 
# fit_rob %>% forecast(h = "1 year")  %>% 
#   filter(is_aggregated(key))

```

```{r}
zri_for_modeling_base <- zri_df %>% filter_index(~"2018-12") %>%
  aggregate_key(State/ Metro / City/ zip, zri = mean(zri))

fit_base_model <- zri_for_modeling_base %>%
  model(base = ETS(zri,
  opt_crit = "mse")) %>%
  reconcile(
    bu = bottom_up(base),
  )
saveRDS(fit_base_model, file = "fit_base_model.Rds")
forecast_base_model <- fit_base_model %>% forecast(h = "1 year") 


# zri_for_modeling_base_alldates <- zri_df  %>%
  aggregate_key(State/ Metro / City/ zip, zri = mean(zri))


# fabletools::accuracy(rob_plot, zri_VA_full)
test <- fabletools::accuracy(forecast_base_model, zri_for_modeling_base_alldates)
# 
# 
# 
test

mean(test)
# # saveRDS(fit_rob, "model.rds")
# fit_rob %>% components()
# 
# fit_rob %>% forecast(h = "1 year")  %>% 
#   filter(is_aggregated(key))

```

```{r}
zri_for_modeling_full <- zri_df %>% as_tsibble() %>% filter_index(~"2018-12") %>%
  aggregate_key(State/ Metro / City/ zip, zri = mean(zri), 
                percent_white = mean(percent_white),
                percent_black = mean(percent_black),
                percent_asian = mean(percent_asian),
                percent_hispanic = mean(percent_hispanic),
                percent_native_am = mean(percent_native_am),
                percent_other_race = mean(percent_other_race),
                percent_0_17 = mean(percent_0_17),
                percent_18_39 = mean(percent_18_39),
                percent_40_64 = mean(percent_40_64),
                percent_65 = mean(percent_65),
                percent_rental_units_vacant = mean(percent_rental_units_vacant),
                percent_rental_units_occupied = mean(percent_rental_units_occupied),
                percent_graduate_deg = mean(percent_graduate_deg),
                percent_bachelors = mean(percent_bachelors),
                percent_associates = mean(percent_associates),
                percent_highschool = mean(percent_highschool),
                percent_less_highschool = mean(percent_less_highschool),
                percent_commute_public_transport = mean(percent_commute_public_transport),
                percent_commute_less_30 = mean(percent_commute_less_30),
                percent_buildings_less_10_units = mean(percent_buildings_less_10_units),
                percent_buildings_10_19_units = mean(percent_buildings_10_19_units),
                percent_buildings_20_49_units = mean(percent_buildings_20_49_units),
                percent_buildings_50_units = mean(percent_buildings_50_units),
                percent_commute_30_to_59 = mean(percent_commute_30_to_59),
                percent_commute_60_to_89 = mean(percent_commute_60_to_89),
                percent_commute_90_more = mean(percent_commute_90_more),
                percent_new_city = mean(percent_new_city),
                percent_new_unit = mean(percent_new_unit),
                percent_units_owner_occupied = mean(percent_units_owner_occupied),
                median_building_age = mean(median_building_age),
                income_per_capita = mean(income_per_capita),
                poverty_rate = mean(poverty_rate),
                total_pop = mean(total_pop),
                percent_workforce_unemployed = mean(percent_workforce_unemployed),
                percent_work_from_home = mean(percent_work_from_home),
                median_age = mean(median_age),
                percent_female = mean(percent_female),
                gini_index = mean(gini_index),
                percent_not_us_citizen = mean(percent_not_us_citizen),
                bs_total_stations = mean(bs_total_stations),
                bs_total_systems = mean(bs_total_systems),
                has_bike_sharing = mean(has_bike_sharing),
                state_local_perc = mean(state_local_perc))

fit_full_model <- zri_for_modeling_full %>%
  model(base = ETS(zri,
  opt_crit = "mse")) %>%
  reconcile(
    bu = bottom_up(base),
  )
saveRDS(fit_full_model, file = "fit_full_model.Rds")

forecast_full_model <- fit_full_model %>% forecast(h = "1 year") 

# 
zri_for_modeling_full <- zri_df #%>%
  aggregate_key(State/ Metro / City/ zip, zri = mean(zri), 
                percent_white = mean(percent_white),
                percent_black = mean(percent_black),
                percent_asian = mean(percent_asian),
                percent_hispanic = mean(percent_hispanic),
                percent_native_am = mean(percent_native_am),
                percent_other_race = mean(percent_other_race),
                percent_0_17 = mean(percent_0_17),
                percent_18_39 = mean(percent_18_39),
                percent_40_64 = mean(percent_40_64),
                percent_65 = mean(percent_65),
                percent_rental_units_vacant = mean(percent_rental_units_vacant),
                percent_rental_units_occupied = mean(percent_rental_units_occupied),
                percent_graduate_deg = mean(percent_graduate_deg),
                percent_bachelors = mean(percent_bachelors),
                percent_associates = mean(percent_associates),
                percent_highschool = mean(percent_highschool),
                percent_less_highschool = mean(percent_less_highschool),
                percent_commute_public_transport = mean(percent_commute_public_transport),
                percent_commute_less_30 = mean(percent_commute_less_30),
                percent_buildings_less_10_units = mean(percent_buildings_less_10_units),
                percent_buildings_10_19_units = mean(percent_buildings_10_19_units),
                percent_buildings_20_49_units = mean(percent_buildings_20_49_units),
                percent_buildings_50_units = mean(percent_buildings_50_units),
                percent_commute_30_to_59 = mean(percent_commute_30_to_59),
                percent_commute_60_to_89 = mean(percent_commute_60_to_89),
                percent_commute_90_more = mean(percent_commute_90_more),
                percent_new_city = mean(percent_new_city),
                percent_new_unit = mean(percent_new_unit),
                percent_units_owner_occupied = mean(percent_units_owner_occupied),
                median_building_age = mean(median_building_age),
                income_per_capita = mean(income_per_capita),
                poverty_rate = mean(poverty_rate),
                total_pop = mean(total_pop),
                percent_workforce_unemployed = mean(percent_workforce_unemployed),
                percent_work_from_home = mean(percent_work_from_home),
                median_age = mean(median_age),
                percent_female = mean(percent_female),
                gini_index = mean(gini_index),
                percent_not_us_citizen = mean(percent_not_us_citizen),
                bs_total_stations = mean(bs_total_stations),
                bs_total_systems = mean(bs_total_systems),
                has_bike_sharing = mean(has_bike_sharing),
                state_local_perc = mean(state_local_perc))

  
  
fabletools::accuracy(forecast_full_model, zri_for_modeling_full)$RMSE  
  # 
# 
# # fabletools::accuracy(rob_plot, zri_VA_full)
test <- na.omit(fabletools::accuracy(forecast_full_model, zri_for_modeling_full)$RMSE)


# 
mean(test)
# # saveRDS(fit_rob, "model.rds")
# fit_rob %>% components()
# 
# fit_rob %>% forecast(h = "1 year")  %>% 
#   filter(is_aggregated(key))

```
saveRDS(data, file = "data.Rds")
data.copy <- readRDS(file = "data.Rds")


```{r}
zri_most <- zri_df_full %>%
  filter(State != "CA" & State == "NY") %>% filter_index(~"2017-12") %>%
  aggregate_key(State / zip, avg_rent = mean(avg_rent))

fit_rob <- zri_most %>%
  model(base = ETS(avg_rent,
  opt_crit = "mae")) %>%
  reconcile(
    bu = bottom_up(base),
  )

rob_plot <- fit_rob %>% forecast(h = "1 year") 


zri_most_full <- zri_df_full %>%
  filter(State != "CA" & State == "NY")  #%>% filter(zip == "22201")
# # rob_plot %>% filter(zip == "22201")%>% autoplot(zri_VA_22201)

test <- na.omit(fabletools::accuracy(rob_plot, zri_most_full)$RMSE)

mean(test)




```



```{r}

zri_VA <- full_df %>%
  filter(State == "VA")

zri_VA <- zri_VA %>% as_tsibble(key = c(zip)) %>% tsibble::fill_gaps()
zri_VA %>% as_tsibble() %>%
  ggplot2::autoplot(avg_rent)

```

```{r}
zri_VA <- full_df %>%
  filter(State == "VA")
VA_plot <- zri_VA %>% filter_index(~"2017-12")

fit_VA <- VA_plot %>%
  model(
    ets = ETS(avg_rent ~ state_local_perc + error("M") + trend(method = c("N", "A", "Ad")) + season(method = c("N", "A", "M"))),
    arima = ARIMA(avg_rent),
    
  )
fit_VA

fit_VA %>%
  glance()
```


```{r}
fc <- fit_VA %>% filter(zip == "22031") %>%
  forecast(h = "1 year")
fc
```

```{r}
zri_VA <- zri_VA %>% filter(zip == "22031")
fc %>% autoplot(zri_VA)
```


```{r}

zri_IL <- full_df %>%
  filter(State == "IL")
zri_IL_leveled <- zri_IL %>%
  aggregate_key((City/zip), mean_rent = mean(avg_rent), taxes = mean(state_local_perc))

fit <- zri_IL_leveled %>%
  filter_index(~"2018-01") %>%
  model(ets = ETS(mean_rent ~ taxes))

# + error("M") + trend(method = c("N", "A", "Ad")) + season(method = c("N", "A", "M")))) # %>%
  reconcile(
    bu = bottom_up(base),
    ols = min_trace(base, method = "ols"),
    # mint = min_trace(base, method = "mint_shrink"),
)

```

```{r}
accuracy(fit)
```

```{r}
fc <- fit %>% forecast(h = "1 year")
fc

```

```{r}
fc %>%
  # filter(is_aggregated(State), is_aggregated(City)) %>%
  autoplot(
    zri_IL_leveled 
  ) +
  facet_wrap(vars(zip), scales = "free_y")



# zri_VA <- zri_VA %>% filter(zip == "22031")
autoplot(fc %>% filter(zip == "60606")) 

%>% autoplot(zri_IL)
```



```{r}
zri_FL <- full_df %>%
  filter(State == "FL")
zri_FL_leveled <- zri_FL %>%
  aggregate_key((City/zip), mean_rent = mean(avg_rent), taxes = mean(state_local_perc))

fit <- zri_FL_leveled %>%
  filter_index(~"2018-01") %>%
  model(ets = ETS(mean_rent ~ taxes))

fc <- fit %>% forecast(h = "1 year")
fc


fc %>%
  # filter(is_aggregated(State), is_aggregated(City)) %>%
  autoplot(
    zri_IL_leveled 
  ) +
  facet_wrap(vars(zip), scales = "free_y")

# 
# 
# # zri_VA <- zri_VA %>% filter(zip == "22031")
# autoplot(fc %>% filter(zip == "60606")) 

```

